---
title: "Coursera Task"
author: "I"
date: "3 10 2020"
output: html_document
---

## get started

```{}
library(caret)
library(rio)
training <- import("pml-training.csv")
testing <- import("pml-testing.csv")
```

## checking length


```{}
dim(training)
dim(testing)
```

##checking data structure 

```{r}
str(training)
```

##Removing NA´s for the next step
```{r}
training_without_na<- training[apply(training, 2, function(x) any(is.na(x))) == FALSE]
```

##Converting "classe" as factor variable 
```{r}
training_without_na$classe <- as.factor(training_without_na$classe)
```

#Feature Selection with boruta algorithm (Boruta goes well, if you want to use random forest later)
```{r}
#install.packages('Boruta')
library(Boruta)

```

#relevant variables for model fitting
```{r}
Boruta_importand <- Boruta(data = training_without_na, classe ~., doTrace =  0)
```

#Get significant variables 
```{r}
boruta_signif <- getSelectedAttributes(Boruta_importand)
print(boruta_signif)
```

# Variable Importance Scores
```{r}
imps <- attStats(Boruta_importand)
imps2 = imps[imps$decision != 'Rejected', c('meanImp', 'decision')]
head(imps2[order(-imps2$meanImp), ])  # descending sort
```

# Plot variable importance
```{r}
plot(Boruta_importand, cex.axis=.7, las=2, xlab="", main="Variable Importance") 
```

#model building with most important variables
```{r}
modFit <- train(classe ~ raw_timestamp_part_1 + cvtd_timestamp + roll_belt + yaw_belt + pitch_belt,
                method = "rf", 
                data =  training_without_na)
```

#predict test set
```{r}
predtest <- predict(modFit, testing)
```

#Results: B A B A A E D B A A B C B A E E A B B B

#Accuracy
```{r}
summary(modFit) #Accuracy by mtry = 23 0.9975094
```













